Football Championship Ticket Options

### 2018-09-16 paper.Rmd
near final paper updates

```{r}
knitr::kable(postResample(pred = testModVol, obs = testDatVol$volLL))
```

@@

```{r}
knitr::kable(postResample(pred = testModPrice, obs = testDatPrice$LL_price))
```

>>>>

```{r}
knitr::kable(postResample(pred = testModVol, obs = testDatVol$volLL), col.names = "")
```

@@

```{r}
knitr::kable(postResample(pred = testModPrice, obs = testDatPrice$LL_price), col.names = "")
```
